Forschungsprojekt

### 2020-10-12 documentation/presentation/main.tex
Vortrag zeug

\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{tikz}
\usetikzlibrary{positioning}

@@

@@

\begin{document}

\section{Introduction}
Graphs are growing fast and are becoming increasingly popular. Many problems can be modeled and solved using graphs.

@@

\clearpage
\section{Preliminaries}
\begin{multicols}{2}
A \emph{weighted, directed graph} is the pair $G=(V,E,w)$ where the \emph{vertex set} is $V\subseteq\mathbb N$ and the $E$ is the \emph{edge set} with
	\begin{equation*}
	  E\subseteq\{(x,y)\,|\, x,y\in V, x\neq y\}
	\end{equation*}
	and $w:E\rightarrow \mathbb R$ is a mapping of edge to a weight.

	\begin{tikzpicture}
		\node[circle, draw] (a) at (0,0) {A};
		\node[circle, draw] (b) at (2,0) {B};
		\node[circle, draw] (c) at (4,0) {C};
		\node[circle, draw] (d) at (0,2) {D};
		\node[circle, draw] (e) at (2,2) {E};

		\draw[-stealth, bend right, line width=1pt] (a) edge (b);
		\draw[-stealth, bend right, line width=1pt] (a) edge (c);

		\draw[-stealth, bend right, line width=1pt] (b) edge (a);
		\draw[-stealth, line width=1pt] (b) -- (d);
		\draw[-stealth, line width=1pt] (b) -- (e);

		\draw[-stealth, line width=1pt] (c) -- (e);

		\draw[-stealth, line width=1pt] (e) -- (a);
	\end{tikzpicture}

@@

	Algorithms:
\begin{itemize}
	\item Single-Source Shortest-Paths (SSSP) is the problem of finding the shortest path from a starting vertex to every other vertex in the input graph.

	\item Breadth-first search (BFS) is a search problem on a graph.

	\item PageRank (PR) is a link analysis algorithm that weighs the vertices of a graph, measuring the vertices relative importance within the graph

\end{itemize}
\end{multicols}

\clearpage
\section{Push \& Pull}

@@

SSSP, BFS, PR, Push/Pull, Hugepages

@@

Outlook:
Immer wieder solche Tests machen, viele der Frameworks ändern sich immer wieder weiter und so, nicht wahr.
\end{document}

>>>>

\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{biblatex}
\usepackage{tikz}
\usetikzlibrary{positioning}

@@

\bibliography{bib.bib}

@@

\begin{document}
% Ich weiß, dass es die Beamer-Klasse gibt.
% Lasst mich doch alle in Ruhe!
% Die hier hatte ich noch rumliegen, das muss jetzt reichen.
\section{Introduction}
Graphs are growing fast and are becoming increasingly popular. Many problems can be modeled and solved using graphs.

@@

\clearpage
\section{Preliminaries}
\begin{multicols}{2}
\noindent
	A \emph{weighted, directed graph} is the tuple $G=(V,E,w)$ where the \emph{vertex set} is $V\subseteq\mathbb N$ and the $E$ is the \emph{edge set} with
	\begin{equation*}
	  E\subseteq\{(x,y)\,|\, x,y\in V, x\neq y\}
	\end{equation*}
	and $w:E\rightarrow \mathbb R$ is a mapping of edge to a weight.

	\begin{center}
	\begin{tikzpicture}
		\node[circle, draw] (a) at (1.7,0) {A};
		\node[circle, draw] (b) at (0,2) {B};
		\node[circle, draw] (c) at (4,0) {C};
		\node[circle, draw] (d) at (0,4) {D};
		\node[circle, draw] (e) at (2.5,2) {E};

		\draw[->, bend right, line width=1pt] (a) edge (b);
		\draw[->, bend right, line width=1pt] (a) edge (c);

		\draw[->, bend right, line width=1pt] (b) edge (a);
		\draw[->, line width=1pt] (b) edge (d);
		\draw[->, line width=1pt] (b) edge (e);

		\draw[->, line width=1pt] (c) edge (e);

		\draw[->, line width=1pt] (e) edge (a);

		\node at (2.5,3) {$w(x)=1\ \forall x\in V$};
	\end{tikzpicture}
	\end{center}

@@

	\subsection{Algorithms}
	\begin{description}
		\item[Single-Source Shortest-Paths (SSSP):] find the shortest path from a starting vertex to every other vertex

		\item[Breadth-first search (BFS):] find a node outgoing from a starting vertex, by increasing maximum hop count step-wise

		\item[PageRank (PR):] link analysis algorithm; weighs vertices, measuring their relative importance
	\end{description}
\end{multicols}

\clearpage
\begin{multicols}{2}
\section{Push Style}
\begin{center}
\begin{tikzpicture}
	\node[circle, draw] (a) at (1.5,1.2) {\bf A};
	\node[circle, draw] (b) at (0,0) {B};
	\node[circle, draw] (c) at (3,0) {C};
	\node[circle, draw] (d) at (1.5,3) {D};

	\draw[->, line width=1pt] (a) edge node[midway, above] {1} (b);
	\draw[->, line width=1pt] (a) edge node[midway, above] {1} (c);
	\draw[->, line width=1pt] (a) edge node[midway, right] {1} (d);
\end{tikzpicture}
\end{center}
\begin{itemize}
	\item reads active vertex, writes neighborhood 
	\item more efficient, if only few active vertices at the same time
	\item more efficient, if neighborhoods do not overlap
\end{itemize}

\columnbreak
\section{Pull Style}
\begin{center}
\begin{tikzpicture}
	\node[circle, draw] (a) at (1.5,1.2) {\bf A};
	\node[circle, draw] (b) at (0,0) {B};
	\node[circle, draw] (c) at (3,0) {C};
	\node[circle, draw] (d) at (1.5,3) {D};

	\draw[->, line width=1pt] (b) edge node[midway, above] {3} (a);
	\draw[->, line width=1pt] (c) edge node[midway, above] {2} (a);
	\draw[->, line width=1pt] (d) edge node[midway, right] {6} (a);
\end{tikzpicture}
\end{center}
\begin{itemize}
	\item reads neighborhood, writes active vertex
	\item[$\rightarrow$] only one write and many read operations
	\item less synchronization in parallel implementations needed
	\item more efficient, if many vertices active at the same time
\end{itemize}
\end{multicols}

@@

@@

Outlook:
Immer wieder solche Tests machen, viele der Frameworks ändern sich immer wieder weiter und so, nicht wahr.

\clearpage
\nocite{unserPaper}
\printbibliography
\end{document}
